---
title: "IDS investigation worksheet"
author: "by Team 26: Shengpeng Qu, Kai Cui, Haipeng Sun, Leo Shen & Leyuan Wen"
date: "`r Sys.Date()`"
output: html_document
---

**Note:** You can use this file as you 'working document' where you can try out various investigation ideas and keep notes about your findings. How you use and structure this file is up to you. It is recommended that you keep notes about what you are investigating and what you find as this will make the process of creating your presentation and report easier. Please note that you _do not_ need to submit this file as part of your group project.



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load-lib, message = FALSE}
library(tidyverse)
# Add any other libraries here



```


```{r load-data}
laptop <- read.csv("data/laptop_data_cleaned.csv") 

# the total number of laptop of each comapny
ggplot(data = laptop, aes(y = Company)) +
  geom_bar()

# the relationship between the company and the price 
ggplot(data = laptop, 
       mapping = aes(y = Price,
                     fill = Company)) +
  geom_histogram() +
  facet_grid( ~Company )

# the relationship between the company and the price ( boxplot ) 
ggplot(data = laptop, 
       mapping = aes(y = Price,
                     fill = Company)) +
  geom_boxplot() +
    facet_grid( ~Company )



# the relationship between the price and the RAM 
ggplot(data = laptop, 
       mapping = aes(y = Price,
                     fill = Ram)) +
  geom_histogram() +
  facet_grid( ~Ram )


   



```


