---
title: "IDS investigation worksheet"
author: "by Team 26: Shengpeng Qu, Kai Cui, Haipeng Sun, Leo Shen & Leyuan Wen"
date: "`r Sys.Date()`"
output: html_document
---

**Note:** You can use this file as you 'working document' where you can try out various investigation ideas and keep notes about your findings. How you use and structure this file is up to you. It is recommended that you keep notes about what you are investigating and what you find as this will make the process of creating your presentation and report easier. Please note that you *do not* need to submit this file as part of your group project.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-lib, message = FALSE}
library(tidyverse)
# Add any other libraries here



```


```{r}

```



```{r load-data}
laptop <- read.csv("data/laptop_data_cleaned.csv") 

# the total number of laptop of each comapny
ggplot(data = laptop, aes(y = Company)) +
  geom_bar() +
  labs(title = " the sales of brands")

# the total number of laptop of each typename
ggplot(data = laptop, aes(y = TypeName)) +
  geom_bar() +
  labs(title = "the sales of different types")

# The market share of different Os
ggplot(laptop, aes(
    x = "",
    fill = Os
    )) +
  geom_bar(position = "fill") +
  coord_polar("y", start = 0) +
  theme_void() +
  labs( title = "The market share of different systems( Os )" )


# the relationship between the company and the price ( boxplot ) 
ggplot(data = laptop, 
       mapping = aes(y = Price,
                     fill = Company)) +
  geom_boxplot()+
  labs(
    x = "Company",
    y = "price depending on all features",
    title = "the relationship between the company and the price"
  )

#
ggplot(data = laptop, 
       mapping = aes(y = Price,
                     fill = TypeName)) +
  geom_boxplot()+
  labs(
    x = "typename",
    y = "price depending on all features",
    title = "the relationship between the typename and the price"
  )


#
ggplot(laptop, 
       mapping = aes(
         x = Weight,   
         y = TypeName
         )) +
  geom_boxplot() +  
  labs(
    x = "Weight",
    y = "TYpe Name",
    title = "The Weight of Different laptop")

#count of different Cpu
ggplot(data = laptop, aes(y =Cpu_brand)) +
  geom_bar() +
  labs(title = " the sales of Cpu")
ggplot(laptop, aes(x = "", fill = Cpu_brand)) +
  geom_bar(position = "fill")+
  coord_polar("y", start = 0)+
  theme_void()
#relationship between the Cpu and Price
ggplot(data = laptop,
       mapping = aes(y = Price,
                     fill = Cpu_brand))+
   geom_histogram()+
  facet_grid(~Cpu_brand)
    

   



```

```{r}
laptop <- read.csv("data/laptop_data_cleaned.csv") 

# price against Ram
laptop %>% 
  ggplot( aes(x = Ram , y = Price))+
  geom_point()+
  geom_smooth(method = "lm", se = FALSE)

# price against weight
laptop %>% 
  ggplot( aes(x = Weight , y = Price))+
  geom_point()+
  geom_smooth(method = "lm", se = FALSE)

# price against touchscreen
laptop %>% 
  ggplot( aes(x = TouchScreen , y = Price))+
  geom_point()+
  geom_smooth(method = "lm", se = FALSE)

# price against Ips
laptop %>% 
  ggplot( aes(x = Ips , y = Price))+
  geom_point()+
  geom_smooth(method = "lm", se = FALSE)

# price against Ppi
laptop %>% 
  ggplot( aes(x = Ppi , y = Price))+
  geom_point()+
  geom_smooth(method = "lm", se = FALSE)

# price against HDD
laptop %>% 
  ggplot( aes(x = HDD , y = Price))+
  geom_point()+
  geom_smooth(method = "lm", se = FALSE)


linear_reg() %>%
  set_engine("lm") %>%
  fit(Price ~ Ram + Weight + TouchScreen + Ips + Ppi + HDD, data = laptop)

```

