---
title: "Project title"
author: "by Team-26: Shengpeng Qu, Kai Cui, Haipeng Sun, Leo Shen & Leyuan Wen"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load-lib, include = FALSE}
library(tidyverse)
# Add any other libraries here



```


```{r load-data, include=FALSE}
# load your data here and any pre-processing/cleaning 
#  that you need for your report.




```


## Research Question

to study the situation in the computer market, the relationship between price, company, the hardware of the computer, and market share.




## Data

The data used by our group is about computers, containing information on thousands of laptops, the dataset encompasses a wide range of brands, models, and configurations. Each laptop entry within the dataset offers a plethora of attributes, such as processor details, memory capacity, storage size, display characteristics, graphics capabilities, battery life, operating system, and more.




## Findings

The data used by our group links to computers, encompassing information on thousands of laptops. The dataset includes a diverse array of brands, models, and configurations. Each laptop entry within the dataset provides a plethora of attributes, such as processor details, memory capacity, storage size, display characteristics, graphics capabilities, battery life, operating system, and more. Our plan is to study the situation in the computer market, focusing on the relationship between price, company, and hardware.

First, we attempt to analyze the situation in the computer market. We use a bar chart to illustrate the market share of each company, as it directly displays the sales data of the brands and facilitates comparisons between them. Lenovo, HP, and Dell emerge as the most popular computer brands in the market, each selling more than 260 units (Lenovo: 289, HP: 268, Dell: 291). Toshiba, MSI, ASUS, and Acer are also popular, with their sales ranging between 50 and 150. In contrast, other brands have minimal sales, with some approaching zero.

Next, we employ the same approach to determine the market share of different categories of computers. Notebooks emerge as the most popular type, with 706 units sold, surpassing the combined sales of all other categories. Gaming, Ultrabook, and 2-in-1 convertible computers also garner significant demand, with sales of 205, 194, and 116 units, respectively. To explore the market share of different operating systems (OS), we use a pie chart. The pie chart is a simple and intuitive visualization that effectively conveys proportional relationships within a relatively straightforward dataset. Unsurprisingly, Windows dominates as the most common operating system, accounting for 1,100 units (86.4%). Mac OS is used by only 21 computers (1.6%), while the remaining 11.9% utilize other operating systems.

Subsequently, we explore the intricate relationship between price, company, and the categories of computers. To clarify these connections, we have designed two comprehensive box plots. The first plot illustrates the price dynamics concerning all features across different companies, while the second plot shows the nuanced relationship between price and the types of computers.

Within the realm of all brands, Razer emerges as the highest average price across all features, boasting a recorded value of 12. Notably, the majority of Razer's products tend to be positioned in a higher price bracket compared to other companies. In contrast, Mediacom, Chuwi, and Vero carve a distinct niche as the three companies are offering the most budget-friendly options, with all their items priced below 10. The remaining companies have a price range between 10 and 11.5, signifying a relatively uniform pricing bracket within this tier.

Furthermore, looking into the boxplots, nine companies, namely Acer, Apple, Asus, Dell, HP, Lenovo, Microsoft, MSI, and Razer, feature elongated boxes, each surpassing a length of 0.5. This extended box length signifies that these companies present customers with a diverse array of choices, reinforcing their popularity and influence within the market. The extended range suggests that these companies cater to a broad spectrum of consumer preferences, enhancing their market appeal.

Moving on to the second box plot, a noteworthy pattern emerges regarding the relationship between price and the type of computers. Workstations exhibit the shortest box, but claim the top spot for the highest average price among the six models. This implies that, in average, workstations command a premium in the market due to their specialized features and capabilities. However, the "network" category stands out with the longest box. Despite boasting the lowest average price, the extended box length indicates a wide variability in netbook prices. Some netbooks within this category surpass the prices of other types, highlighting the pricing dynamics within the market.








## References

List any references here. You should, at a minimum, list your data source.


