---
title: "Project title"
author: "by Team-26: Shengpeng Qu, Kai Cui, Haipeng Sun, Leo Shen & Leyuan Wen"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load-lib, include = FALSE}
library(tidyverse)
# Add any other libraries here



```


```{r load-data, include=FALSE}
# load your data here and any pre-processing/cleaning 
#  that you need for your report.




```


## Research Question

To study the computer market and understand the relationship between price, company dynamics, computer hardware, and market share, it is essential to follow a systematic approach.




## Data

The data used by our group links to computers, encompassing information on thousands of laptops. The dataset provides a wide range of brands, models, and configurations. Each laptop entry within the dataset provides several specifications, such as processor details, memory capacity, storage size, display characteristics, graphics capabilities, battery life, operating system, and more.

## Finding

The data used by our group is about computers and includes information on thousands of laptops. This dataset features laptops from multiple brands and models with different configurations and characteristics. Each entry in the dataset offers detailed attributes on its processor details, memory capacity, storage size, width ratio, display characteristics, graphic capabilities, battery life, operating system as well as battery life information. Our plan is to conduct an in-depth examination of the computer market by studying its relationship between price, amrket share, company, and hardware.

First we attempt to analyze its state with the use of bar charts as visual aids. Market information of each company can be easily assessed as it displays sales data for all brands in direct comparisons with each other. Lenovo, HP and Dell stand out as being popular computer brands on the market with each selling over 260 units (Lenovo: 289; HP: 268, Dell: 269). Toshiba, MSI, ASUS and Acer brands also command significant market presence with sales between 50 to 150. In contrast, other brands experience much smaller volumes, some even approaching zero.

Next, We employ this same method of analysis when determining market shares across categories of computers. Notebook computers remain the top choice, selling 706 units compared to all other categories combined. Gaming, Ultrabook, and 2-in-1 convertible computers also have significant demand, with sales of 205, 194, and 116 units, respectively. To explore the market share of different operating systems (OS), we use a pie chart. The pie chart is a simple and intuitive visualization that effectively conveys proportional relationships within a relatively straightforward dataset. Unsurprisingly, Windows dominates as the most common operating system, accounting for 1,100 units (86.4%). Mac OS is used by only 21 computers (1.6%), while the remaining 11.9% utilize other operating systems. 

Subsequently, we explore the intricate relationship between price, company, and the categories of computers. To clarify these connections, we have designed two comprehensive box plots. The first plot illustrates the price dynamics concerning all features across different companies, while the second plot shows the nuanced relationship between price and the types of computers. Within the realm of all brands, Razer emerges as the highest average price across all features, boasting a recorded value of 12. Notably, the majority of Razer's products tend to be positioned in a higher price bracket compared to other companies. In contrast, Mediacom, Chuwi, and Vero carve a distinct niche as the three companies are offering the most budget-friendly options, with all their items priced below 10. The remaining companies have a price range between 10 and 11.5, signifying a relatively uniform pricing bracket within this tier. 

Furthermore, looking into the boxplots, nine companies, namely Acer, Apple, Asus, Dell, HP, Lenovo, Microsoft, MSI, and Razer, feature elongated boxes, each surpassing a length of 0.5. This extended box length signifies that these companies present customers with a diverse array of choices, reinforcing their popularity and influence within the market. The extended range suggests that these companies cater to a broad spectrum of consumer preferences, enhancing their market appeal. 

Moving on to the second box plot, a noteworthy pattern emerges regarding the relationship between price and the type of computers. Workstations exhibit the shortest box, but claim the top spot for the highest average price among the six models. This implies that, in average, 
workstations command a premium in the market due to their specialized features and capabilities. However, the "network" category stands out with the longest box. Despite boasting 
the lowest average price, the extended box length indicates a wide variability in netbook prices. Some netbooks within this category surpass the prices of other types, highlighting the pricing dynamics within the market.

The final box plot illustrates the weight distribution, central tendency, shape of the data, and weight variability among laptops in various categories (Workstation, Ultrabook, 
Notebook, Netbook, Gaming, 2 in 1 Convertible). It aids in identifying outliers and assessing the size of data sets. The shape of the data is exceptional. 

In each product category, the maximum value is determined by the third quartile, while the boxplot identifies the minimum value by the first quartile, and the average value is represented by the vertical line in the middle. Gaming laptops and Workstation exhibit the widest weight distribution, ranging from 2.8kg to 3.6kg and 2kg to 3kg, respectively. In contrast, Netbooks demonstrate the most concentrated weight distribution in the 1kg to 1.5kg range. Based on average weight, Netbooks and Ultrabooks appear relatively light, while Gaming and Workstation laptops are comparatively heavy. Outliers, especially found in Notebooks, need additional attention. Further analysis is essential to determine whether these outliers result from data quality issues or are characteristic of the investigated product. Insights can be gleaned by examining the distribution of different laptop weights.

In the laptop market, CPU type is one of the most crucial factors influencing consumers' purchasing decisions. To visually understand the sales of laptops with different CPU types, we analyzed the data using three graphs.

Firstly, laptops were categorized into five groups based on CPU type: i7, i5, i3, AMD, and other Intel types. By plotting a bar chart, it was observed that i7 had the highest sales volume, then followed by i5, with AMD having the lowest sales. This finding was further confirmed by the pie chart.

Moving on, a histogram was created to explore the relationship between CPU type and price. It was observed that the other Intel CPU types exhibited the largest price range, covering almost all price brackets. However, the highest sales volume was still associated with products priced around 9.6. This suggests that consumers may prioritize the price factor more when purchasing laptops containing other Intel CPUs.

In terms of data, i7 and i5 emerged as the more mainstream CPU types. i7 primarily caters to the mid-to-high-end market and is, on average, the most expensive. Conversely, i5 mainly targets the mid-range market. Despite being slightly less powerful than i7, it is priced a bit lower on average. The sales volume data indicates that i7 is likely the preferred choice among consumers due to its superior performance. While i5 is slightly less powerful than i7 and has a somewhat lower average price, its sales volume suggests that its performance still satisfies the needs of a significant portion of consumers. As for i3, it is particularly used in low-end and mid-range computers. Its sales lag behind i7 and i5, possibly due to its comparatively lower performance, despite having a relatively low average price.

It's noteworthy that the sales volume of AMD CPUs is relatively low, even though their coverage is second only to other Intel types. This may indicate lower consumer awareness and acceptance of AMD CPUs.

In addition to those, we made some linear regression to express further relationship.

From the chart which compares HDD capacity and price, data points are widely dispersed but the trend line remains relatively level, suggesting that regardless of how HDD capacity varies (from 0GB up to 2000GB), prices remain within an extremely narrow fluctuation range between 9-12. This may suggest that in modern laptop markets increasing HDD capacity does not result in significant price hikes as may have previously been anticipated; perhaps due to consumer preference for SSDs or their being part of less costly overall systems.

Memory (RAM) and price show an increasingly positive correlation, and laptops with 4GB RAM typically sell for an average selling price around 10, while those equipped with 32GB of RAM or greater often reach 14+. This trend suggests that increasing RAM enhances value considerably in an environment with rising performance requirements.

The chart depicting the effects of weight on price shows an incrementally positive trend as weight increases (from 1kg to 4kg). This could be explained by heavier laptops typically featuring larger displays, more powerful processors, higher performing graphics cards and additional cooling systems which all are typically costlier components. 

The following chart displays how touchscreen functionality impacts price. Unfortunately, its impact does not show a substantial price advantage for laptops with touchscreen functionality; perhaps reflecting that market expectations regarding touchscreen functionality have already been factored into consumer decisions and it no longer plays such an influential role. 

The next chart illustrates the impact of having or lacking an IPS display on price. According to data provided, price distribution remains roughly constant regardless of a laptop being equipped with one, suggesting IPS screens have become part of standard offerings and no longer serve as 
primary price differentiators. 

Finally, a chart on the relationship between PPI and price demonstrates a clear trend: laptops with higher resolution screens tend to be pricier. We can observe as PPI increases so do prices, especially from 200-300 where prices jump significantly (from approximately 10-12). This highlights market demand and willingness to pay extra for high definition displays. After reviewing these data points, our conclusion is that while storage capacity and touchscreens 
no longer play such an essential role in laptop pricing strategies, performance-related specs such as RAM and high-resolution displays remain key price drivers. An increase in weight may reflect additional features or functionality within a laptop but its impact is relatively minor on price.






## References

List any references here. You should, at a minimum, list your data source.


